---
title: "The SNU ALS Registry Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar:
      - { title: "Interactive Case Review", href: "https://yoonhohong.shinyapps.io/ALSregistry2/"}
    social: menu
    source_code: https://github.com/snuals/registrydashboard
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(pier)
```

```{r}
source("global.R")
```

Baseline
==================================================================

Row
------------------------------------------------------------------

### Number of MND patients enrolled as of `r date_update_registry`

```{r}
valueBox(dim(baseline)[1], icon = "fa-user")
```

### Number of ALS patients enrolled as of `r date_update_registry`

```{r}
valueBox(dim(als)[1], icon = "fa-user")
```

### Number of ALS patients who died or got tracheostomy

```{r}
valueBox(dim(time_df_close[!is.na(time_df_close$Date_death_tracheo),])[1], icon = "fa-user")
```


Row
-----------------------------------------------------------------------

### Enrollment by month (since 2017-01)
```{r}
ggplotly(plot_enrollment_month)
```

### MND types
```{r}
plot_mnd_type
```

Row
-----------------------------------------------------------------------
### Sex
```{r}
plot_sex
```

### Age distribution at diagnosis (ALS)
```{r}
ggplotly(plot_age)
```

Row
----------------------------------------------------------------------
### Onset region
```{r}
plot_onset_region
```

### Time between onset, diagnosis, enrollment and the first visit  
```{r}
ggplotly(plot_time_initial)
```

Follow-up
============================


Row
--------------------------


### Distribution of FU duration 
```{r}
ggplotly(plot_fu_duration)
```


### Time from the 1st to the latest visit
```{r}
plot_fu_duration_pie
```
 


Row
---------
### ALSFRS Trajectory 
```{r}
ggplotly(plot_alsfrs)
```

Row
--------
### Weight Trajectory
```{r}
ggplotly(plot_wt)
```

### FVC Trajectory
```{r}
ggplotly(plot_FVC_percent)
```

Event & Close  
====================

Row 
------------------
### Gastrostomy 
```{r}
gauge(event_df[event_df$Event == "Gastrostomy",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```

### NIV
```{r}
gauge(event_df[event_df$Event == "NIV",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```

### Tracheostomy 
```{r}
gauge(event_df[event_df$Event == "Tracheostomy",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```


Row 
------------------

### Death  
```{r}
gauge(close_df[close_df$Event == "Death",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```

### Refer  
```{r}
gauge(close_df[close_df$Event == "Refer",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```

### Lost to f/u  
```{r}
gauge(close_df[close_df$Event == "Lost to f/u",]$Prop, min = 0, max = 100, symbol = '%', gaugeSectors(success = c(20, 100), warning = c(10, 19), danger = c(0, 9)))
```


Row 
-----------

### Term definition

*Close refers to the end of all tracking attempts, which includes death, refer, and lost to f/u*   
*Note that this does not apply to the patients who are under tracking by any means (for example, phone)*   

**Lost to fu**    
should meet all the followings.   
- not visited for the recent 6 months, and    
- can not be contacted (by phone) or the patient refused to participate the registry any longer.   

**Refer**   
should meet all the followings.    
- referred to local hospital, and   
- can not be contacted (by phone) or the patient refused to participate the registry any longer.      

**Note**    
Patients who were referred to local hospital should be contacted regularly (every 3 month) by phone, and the occurence of major events (gastrostomy, NIV, tracheostomy, death) should be tracked.          


### Time from onset to event (months)
```{r}
ggplotly(plot_event1)
```


### KM survival curve 
```{r}
plot_survival
```


Row
---------------

### Time from the latest visit (months): Barplot       
```{r}
ggplotly(plot_latestVisit2now)
```

### Time from the latest visit (months): Pie chart  

```{r}
plot_latestVisit2now_gr
```


Biorepository 
======================

Row
----------------------- 

### Serum (# of patients)  
```{r}
valueBox(length(unique(ser$Study_ID)))
```

### Plasma (# of patients) 
```{r}
valueBox(length(unique(pla$Study_ID)))
```

### CSF (# of patients)
```{r}
valueBox(length(unique(csf$Study_ID)))
```

### Buffy coat (# of patients) 
```{r}
valueBox(length(unique(buf$Study_ID)))
```

Row {data-height=300}
----------------------------   

### Serum 
```{r}
plot_ser
```

### Plasma 
```{r}
plot_pla
```

### CSF 
```{r}
plot_csf
```

### Buffy coat 
```{r}
plot_buf
```

















